---
title: "final project EDA"
author: "Peijin Li"
date: "2023-05-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library('igraph')
library('ggplot2')
library(ggplot2)
library(readxl)
require("statnet")
require("ergm")
require("intergraph")
require("netseg")
```

```{r, warning=FALSE, include=FALSE}
dataFacebook <- read_excel("Facebook_Data.xlsx")
#dataInstagram <- read_excel("Instagram_Data.xlsx")
#dataTwitter <- read_excel("Twitter_Data.xlsx")
UserNodes <- dataFacebook[,c(1:1)]
names(UserNodes)<-c('V1')  
```

```{r}
#Load Network Edgelist from .csv
Facebook_matrix <- read.csv("Facebook_Data.csv", skip=1, header=FALSE)
Facebook_matrix <- as.matrix(Facebook_matrix)
FacebookNetwork <- graph_from_adjacency_matrix(Facebook_matrix, mode = "undirected")
```

```{r}
#Load Network Edgelist from .csv
Instagram_matrix <- read.csv("Instagram_Data.csv", skip=1, header=FALSE)
Instagram_matrix <- as.matrix(Instagram_matrix)
InstagramNetwork <- graph_from_adjacency_matrix(Instagram_matrix, mode = "undirected")
```

```{r}
Twitter_matrix <- read.csv("Twitter_Data.csv", skip=1, header=FALSE)
Twitter_matrix <- as.matrix(Twitter_matrix)
TwitterNetwork <- graph_from_adjacency_matrix(Twitter_matrix, mode = "undirected")
```


Calculate each of the following for each network:
1.Average degree
2.Density (state whether you are calculating for directed or undirected for each data set)
3.Number of components
4.Degree distribution (show in plot)
5.Diameter of Largest Component

```{r}
# Check the number of vertices and edges
vcount(FacebookNetwork)
ecount(FacebookNetwork)
ecount(InstagramNetwork)
ecount(TwitterNetwork)
```

```{r}
# Check the diameter
diameter(FacebookNetwork)
diameter(InstagramNetwork)
diameter(TwitterNetwork)
```
```{r}
# Check the clustering coefficient
transitivity(FacebookNetwork)
transitivity(InstagramNetwork)
transitivity(TwitterNetwork)
```



```{r}
avg_degree_F <- mean(igraph::degree(FacebookNetwork))
# Print the result
cat("The average degree of FacebookNetwork is", avg_degree_F)

avg_degree_F <- mean(igraph::degree(InstagramNetwork))
# Print the result
cat("The average degree of InstagramNetwork is", avg_degree_F)

avg_degree_F <- mean(igraph::degree(TwitterNetwork))
# Print the result
cat("The average degree of TwitterNetwork is", avg_degree_F)
```

```{r}
#The density of a graph is the ratio of the number of edges and the number of possible edges.
# It is undirected density
density_F <- edge_density(FacebookNetwork, loops = FALSE)
# Print the result
cat("The density of FacebookNetwork is", density_F)

density_F <- edge_density(InstagramNetwork, loops = FALSE)
# Print the result
cat("The density of InstagramNetwork is", density_F)

density_F <- edge_density(TwitterNetwork, loops = FALSE)
# Print the result
cat("The density of TwitterNetwork is", density_F)
```

```{r}
count_components_F <- count_components(FacebookNetwork)
# Print the result
cat("The number of components of FacebookNetwork is", count_components_F)

count_components_F <- count_components(InstagramNetwork)
# Print the result
cat("The number of components of InstagramNetwork is", count_components_F)

count_components_F <- count_components(TwitterNetwork)
# Print the result
cat("The number of components of TwitterNetwork is", count_components_F)
```

```{r}
#degree_distribution(FlorentineNetwork)
## plot the degree_distribution
t1= table(degree(FacebookNetwork))
relafreq_1 <- t1/sum(t1)
barplot(relafreq_1, xlab = "Degree", ylab = "Relative frequencies", 
        main = "Degree Distribution of FacebookNetwork",
        col = "plum",
        ylim = c(0, max(relafreq_1)))
```

```{r}
t1= table(degree(InstagramNetwork))
relafreq_1 <- t1/sum(t1)
barplot(relafreq_1, xlab = "Degree", ylab = "Relative frequencies", 
        main = "Degree Distribution of InstagramNetwork",
        col = "plum",
        ylim = c(0, max(relafreq_1)))
```

```{r}
t1= table(degree(TwitterNetwork))
relafreq_1 <- t1/sum(t1)
barplot(relafreq_1, xlab = "Degree", ylab = "Relative frequencies", 
        main = "Degree Distribution of TwitterNetwork",
        col = "plum",
        ylim = c(0, max(relafreq_1)))
```


```{r}
#pak::pkg_install("fangzhou-xie/rethnicity")
```


```{r}
# Print the result
diameter_F <- diameter(FacebookNetwork)
cat("The diameter of largest component of FacebookNetwork is", diameter_F)

diameter_F <- diameter(InstagramNetwork)
cat("The diameter of largest component of FacebookNetwork is", diameter_F)

diameter_F <- diameter(TwitterNetwork)
cat("The diameter of largest component of FacebookNetwork is", diameter_F)
```

#####################################################################################################################################
Centrality Analysis 
########################################################
1.What member has the highest level of betweenness centrality?
2.Show a correlation (scatter) plot of betweenness centrality and degree centrality.
3.In 1-2 sentences, describe why (and if) the highest betweenness node might be important to the overall graph structure.
```{r}
# Calculate the betweenness centrality
bc0 <- igraph::betweenness(FacebookNetwork)

# Find the member with the highest betweenness centrality
highest_bc_member0 <- which.max(bc0)

# Print the result
cat("The member with the highest betweenness centrality is", highest_bc_member0)


# Calculate the betweenness centrality
bc1 <- igraph::betweenness(InstagramNetwork)

# Find the member with the highest betweenness centrality
highest_bc_member1 <- which.max(bc1)

# Print the result
cat("The member with the highest betweenness centrality is", highest_bc_member1)



# Calculate the betweenness centrality
bc2 <- igraph::betweenness(TwitterNetwork)

# Find the member with the highest betweenness centrality
highest_bc_member2 <- which.max(bc2)

# Print the result
cat("The member with the highest betweenness centrality is", highest_bc_member2)
```

```{r}
typeof(bc0)
order(bc0,decreasing = TRUE)[1:10]
order(bc1,decreasing = TRUE)[1:10]
order(bc2,decreasing = TRUE)[1:10]
```

```{r}
UserNodes[order(bc0,decreasing = TRUE)[1:10],]
UserNodes[order(bc1,decreasing = TRUE)[1:10],]
UserNodes[order(bc2,decreasing = TRUE)[1:10],]
```


```{r}
# Calculate degree centrality
dc0 <- igraph::degree(FacebookNetwork)

# Calculate betweenness centrality
bc0 <- igraph::betweenness(FacebookNetwork)

# Create scatter plot
plot(dc0, bc0, xlab = "Degree Centrality", ylab = "Betweenness Centrality",main = "Correlation of Betweenness Centrality and Degree Centrality  (Facebook)")

#df1_0 <- as.data.frame(dc0)
#df2_0 <- as.data.frame(bc0)

#df3_0 <- cbind(df1_0, df2_0)

##########
# Calculate degree centrality
dc1 <- igraph::degree(InstagramNetwork)

# Calculate betweenness centrality
bc1 <- igraph::betweenness(InstagramNetwork)

#df1_1 <- as.data.frame(dc1)
#df2_1 <- as.data.frame(bc1)
#df3_1 <- cbind(df1_1, df2_1)

# Create scatter plot
plot(dc1, bc1, xlab = "Degree Centrality", ylab = "Betweenness Centrality",main = "Correlation of Betweenness Centrality and Degree Centrality (Instagram)")

###########
# Calculate degree centrality
dc2 <- igraph::degree(TwitterNetwork)

# Calculate betweenness centrality
bc2 <- igraph::betweenness(TwitterNetwork)

#df1_2 <- as.data.frame(dc2)
#df2_2 <- as.data.frame(bc2)
#df3_2 <- cbind(df1_2, df2_2)

# Create scatter plot
plot(dc2, bc2, xlab = "Degree Centrality", ylab = "Betweenness Centrality",main = "Correlation of Betweenness Centrality and Degree Centrality  (Twitter)")
```

D.For Florentine Families network:
1.Which family has the highest level of closeness centrality?
2.Show a correlation scatter plot of closeness centrality and degree centrality.
3.In 1-2 sentences, describe why (and if) the highest closeness centrality node might be important to the overall graph structure.

```{r}
# Calculate the closeness centrality
cc0 <- igraph::closeness(FacebookNetwork)

# Find the member with the highest closeness centrality
highest_cc_member0 <- which.max(cc0)
#FlorentineNodes[highest_cc_member,]
#highest_cc_member0
#cat("The family with the highest closeness centrality is", UserNodes[highest_cc_member0,])
#############################################################################
# Calculate the closeness centrality
cc1 <- igraph::closeness(InstagramNetwork)

# Find the member with the highest closeness centrality
highest_cc_member1 <- which.max(cc1)
#FlorentineNodes[highest_cc_member,]
#highest_cc_member1
#cat("The family with the highest closeness centrality is", UserNodes[highest_cc_member0,])
##############################################################################
# Calculate the closeness centrality
cc2 <- igraph::closeness(TwitterNetwork)

# Find the member with the highest closeness centrality
highest_cc_member2 <- which.max(cc2)
#FlorentineNodes[highest_cc_member,]
#highest_cc_member0
#cat("The family with the highest closeness centrality is", UserNodes[highest_cc_member0,])
#############################################################################


order(cc0,decreasing = TRUE)[1:10]
order(cc1,decreasing = TRUE)[1:10]
order(cc2,decreasing = TRUE)[1:10]
```

```{r}
UserNodes[order(cc0,decreasing = TRUE)[1:10],]
UserNodes[order(cc1,decreasing = TRUE)[1:10],]
UserNodes[order(cc2,decreasing = TRUE)[1:10],]
```

```{r}
# Create scatter plot
plot(dc0, cc0, xlab = "Degree Centrality", ylab = "Closeness Centrality",main = "Correlation of Closeness Centrality and Degree Centrality (Facebook)")
##########################
plot(dc1, cc1, xlab = "Degree Centrality", ylab = "Closeness Centrality",main = "Correlation of Closeness Centrality and Degree Centrality (Instagram)")
############################
plot(dc2, cc2, xlab = "Degree Centrality", ylab = "Closeness Centrality",main = "Correlation of Closeness Centrality and Degree Centrality (Twitter)")
```

```{r}
# Calculate the number of triangles
num_triangles <- sum(triangles(FacebookNetwork))/3
num_triangles 
```



####################################################################################################################################
Ego Network Analysis
#################################################################
B. Create the ego network for the highest degree node of each graph and calculate the following: (Do not include ego in the ego network!)
1.Size of network (node count)
2.Density
3.Number of Components

```{r}
# Find the node with the highest degree
highest_degree_node_F0 <- which.max(igraph::degree(FacebookNetwork))
# Create the ego network for the highest degree node
ego_network_F0 <- make_ego_graph(FacebookNetwork, nodes = highest_degree_node_F0)[[1]]
# Get the node count of the ego network (excluding the ego node)
node_count_F0 <- vcount(ego_network_F0) - 1
# Get the Density of the ego network
density_F0 <- edge_density(ego_network_F0)
# Get the Number of Components of the ego network
count_components_F0 <- count_components(ego_network_F0, mode = c("weak", "strong"))

# Print the node count
cat("For KarateClubNetwork:",sep = "")
cat("The node count of the ego network (excluding the ego node) is", node_count_F0)
cat(". The density of the ego network is", density_F0)
cat(". The number of the ego network is", count_components_F0)
```
```{r}
UserNodes[highest_degree_node_F0,]

plot(ego_network_F0,vertex.color = "plum",main = "Largest Ego Network in FacebookNetwork", vertex.size = 7,vertex.label.cex=0.7)
```


```{r}
# Find the node with the highest degree
highest_degree_node_F1 <- which.max(igraph::degree(InstagramNetwork))
# Create the ego network for the highest degree node
ego_network_F1 <- make_ego_graph(InstagramNetwork, nodes = highest_degree_node_F1)[[1]]
# Get the node count of the ego network (excluding the ego node)
node_count_F1 <- vcount(ego_network_F1) - 1
# Get the Density of the ego network
density_F1 <- edge_density(ego_network_F1)
# Get the Number of Components of the ego network
count_components_F1 <- count_components(ego_network_F1, mode = c("weak", "strong"))

# Print the node count
cat("For KarateClubNetwork:",sep = "")
cat("The node count of the ego network (excluding the ego node) is", node_count_F1)
cat(". The density of the ego network is", density_F1)
cat(". The number of the ego network is", count_components_F1)
```

```{r}
UserNodes[highest_degree_node_F1,]

plot(ego_network_F1,vertex.color = "plum",main = "Largest Ego Network in InstagramNetwork", vertex.size = 7,vertex.label.cex=0.7)
```

```{r}
# Find the node with the highest degree
highest_degree_node_F2 <- which.max(igraph::degree(TwitterNetwork))
# Create the ego network for the highest degree node
ego_network_F2 <- make_ego_graph(TwitterNetwork, nodes = highest_degree_node_F2)[[1]]
# Get the node count of the ego network (excluding the ego node)
node_count_F2 <- vcount(ego_network_F2) - 1
# Get the Density of the ego network
density_F2 <- edge_density(ego_network_F2)
# Get the Number of Components of the ego network
count_components_F2 <- count_components(ego_network_F2, mode = c("weak", "strong"))

# Print the node count
cat("For KarateClubNetwork:",sep = "")
cat("The node count of the ego network (excluding the ego node) is", node_count_F2)
cat(". The density of the ego network is", density_F2)
cat(". The number of the ego network is", count_components_F2)
```

```{r}
UserNodes[highest_degree_node_F2,]

plot(ego_network_F2,vertex.color = "plum",main = "Largest Ego Network in TwitterNetwork", vertex.size = 7,vertex.label.cex=0.7)
```

###############################################################################################################
Race Recognition 
############################################################################

```{r, warning=FALSE, include=FALSE}
#install.packages("pak")
#pak::pkg_install("rethnicity")
library(rethnicity)
library(stringr)
```

```{r}
UserNodes <- dataFacebook[,c(1:1)]
names(UserNodes)<-c('V1')  
```

```{r}
#remove all trailing whitespace
UserNodes$clean_V1  <- str_trim(UserNodes$V1, "right")

UserNodes$last_V1 <- word(UserNodes$clean_V1, -1)
```

```{r}
predict_ethn <-predict_ethnicity(lastnames = UserNodes$last_V1, method = "lastname")
predict_ethn
```
```{r}
## prepare the data 
race_plot <- predict_ethn%>% dplyr::count(race)
```

```{r}
# Data
x <- race_plot$race
y <- race_plot$n

# Barplot
bp <- barplot(y, names.arg = x, ylim = c(0, max(y)*1.2), col = "plum",xlab = "Race", ylab = "Number", main = "Race Prediction for the 1,000 users")

# Add text to the bars
text(x = bp, y = y, labels = y, pos = 3)
```

#########################################################################################
Visualize the network with race
####################################################################################

```{r}
# Find the node with the highest degree
highest_degree_node_F0 <- which.max(igraph::degree(FacebookNetwork))
# Create the ego network for the highest degree node
ego_network_F0 <- make_ego_graph(FacebookNetwork, nodes = highest_degree_node_F0)[[1]]
```

```{r}
library(igraph)
```


```{r}
node_names <- nodes(ego_network_F0)$name
```

```{r}
plot(ego_network_F1_updated, vertex.col=V(ego_network_F1_updated)$Race,vertex.color = "plum",main = "Largest Ego Network in FacebookNetwork", vertex.size = 7,vertex.label.cex=0.7)
```

```{r}
# Find the node with the highest degree
highest_degree_node_F1 <- which.max(igraph::degree(InstagramNetwork))
# Create the ego network for the highest degree node
ego_network_F1 <- make_ego_graph(InstagramNetwork, nodes = highest_degree_node_F1)[[1]]

```



#######################################################################################################
ERGM Estimate 
##########################################################################################################

```{r}
library(network)
```

```{r}
V(FacebookNetwork)$Race = predict_ethn$race
V(InstagramNetwork)$Race = predict_ethn$race
V(TwitterNetwork)$Race = predict_ethn$race
```

```{r, warning=FALSE}
## ERGM Estimate 
ERGM_facebook <- ergm(asNetwork(FacebookNetwork)~edges+nodematch('Race')+nodefactor('Race'))
summary(ERGM_facebook)
```

```{r}
## ERGM Estimate 
ERGM_Instagram <- ergm(asNetwork(InstagramNetwork)~edges+nodematch('Race')+nodefactor('Race'))
summary(ERGM_Instagram)
```

```{r}
## ERGM Estimate 
ERGM_Twitter <- ergm(asNetwork(TwitterNetwork)~edges+nodematch('Race')+nodefactor('Race'))
summary(ERGM_Twitter)
```




